An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-16 VLDB2026/main.tex
Update main.tex
change conclusion and challenges

@@

\section{CONCLUSION}

In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries. For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance. We then perform experiments on 6 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth. Additionally, we compare existing range filtering algorithms using 3 range query datasets. Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement. Our study not only validates previous research but also offers insights for future work.

>>>>

\textcolor{blue}{
In our experiments, we found that many range filtering algorithms perform worse than Faiss at high recall (0.95). This shows that the design of current algorithms still needs improvement. We suggest that future range filtering algorithms should include Faiss as a baseline.
}

@@

\section{CONCLUSION}
\textcolor{blue}{
	In this paper, we evaluate various hybrid query methods, including different algorithms, vector databases, and vector libraries. For attribute filtering algorithms, we design and conduct a series of experiments to comprehensively assess their overall performance. To facilitate fair and reproducible comparisons in future research, we enrich existing datasets with attribute values and design a variety of experimental scenarios based on practical needs. We then perform experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms in depth. Additionally, we compare existing range filtering algorithms using 4 range query datasets. Finally, we provide a detailed analysis of the experimental results, summarize key findings, and highlight areas for improvement. Our study not only validates previous research but also offers insights for future work.
}
